Efficient UQ for chemical systems using active \author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan} subspaces

### 2018-07-18 Paper/old.tex
..

\section{Active subspaces and sensitivity analysis}
\label{sec:assa}

@@

>>>>

\documentclass[11pt]{article}

\usepackage{lineno,hyperref}
\usepackage{latexsym,amsthm,amsmath,xcolor,graphicx, amssymb, color,hyperref,booktabs,mathrsfs}

%\modulolinenumbers[5]

\usepackage{geometry}
 \geometry{
 letterpaper,
 total={8.5in,11in},
 left=.75in,
 right=.75in,
 top=.75in,
 bottom=.75in,
 }

% Macros
\renewcommand{\vec}[1]{{\mathchoice
                     {\mbox{\boldmath$\displaystyle{#1}$}}
                     {\mbox{\boldmath$\textstyle{#1}$}}
                     {\mbox{\boldmath$\scriptstyle{#1}$}}
                     {\mbox{\boldmath$\scriptscriptstyle{#1}$}}}}
\newcommand{\norm}[1]{\left\| {#1} \right\|}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\grad}{\nabla}
\newcommand{\hessian}{\nabla^2}
\newcommand{\V}{\mathbb{V}}
\renewcommand{\S}{\mathbb{S}}
\newcommand{\ST}{\mathbb{S}^{\text{tot}}}
\newcommand{\ip}[2]{\langle{#1}, {#2}\rangle}
\newcommand{\tp}{{\!\mathsf{T}}}
\newcommand{\trace}{\mathrm{trace}}
\newcommand{\mat}[1]{\mathbf{{#1}}}
\newcommand{\Np}{{N_\text{p}}}
\newcommand{\E}[1]{\mathrm{E}\left\{{#1} \right\}}

\newcommand{\alennote}[1]{{\color{blue} Alen: {#1}}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{proposition}{Proposition}[section]

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%
\title{Efficient UQ for chemical systems using active 
\author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan}
subspaces}

\begin{document}
\maketitle

\begin{abstract}
Insert abstract here.
\end{abstract}

\tableofcontents
\section{Introduction}

Constributions:
\begin{enumerate}
\item Iterative computation of active subspaces for efficient surrogate modeling 
\item Comparison of gradient-free and gradient based approaches.
\item Perspectives on activity scores as means of approximating DGSMs.
\item Application to challenging chemical kinetics problem. 
\end{enumerate}
Insert introduction here.

\section{Active subspaces and sensitivity analysis}

@@

\section{Method}

\section{Application to $H_2$/$O_2$ reaction mechanism: high-dimensional case}

\alennote{Manav, can we consider a higher dimensional problem with uncertain
activation energies as well?}

\section{Conclusion}

\section*{References}

\bibliography{mybibfile}

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.40\textwidth]{./Figures/comp_eig}
\hspace{1mm}
  \includegraphics[width=0.45\textwidth]{./Figures/comp_eigv}
  \\ \vspace{5mm}
  \includegraphics[width=0.40\textwidth]{./Figures/comp_ssp}
\hspace{1mm}
  \includegraphics[width=0.45\textwidth]{./Figures/comp_as}
  \\ \vspace{5mm}
  \includegraphics[width=0.42\textwidth]{./Figures/ub_conv_kinetics_rich}
\end{center}
\end{figure}

\end{document}
